Hydras \& Co.

### 2023-05-09 doc/chapter-fol.tex
fix a few typos

\begin{remark}
  The constructors of types \texttt{Rel} and \texttt{Fun} are suffixed by an underscore, in order to reserve the names \texttt{a}, \texttt{f}, \texttt{h}, \texttt{R}, etc. to functions which build terms and formulas
(please look at next sections).

@@

\begin{remark}[Variables]
In O'Connor's formalization of first-order logic, the variables are \gallina terms of the form \texttt{var $L$ $i$}, where $L$ is
 a language and $i$ a natural number. 
Although other choices may be considered : PHOAS, de Bruijn indices, etc,  we   respect this representation, in order not to break long proof scipts which use this representation (please look at \cite{OConnor05} for a related discussion).

@@

\begin{remark}
 We can use \coq's \texttt{Notation} features to print and parse terms in a more readable form.

@@

@@

From href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}
\inputsnippets{fol/folScope}

@@

@@

\begin{remark}[bound variables]
\inputsnippets{FolExamples/boundVars}  
\end{remark}

>>>>

\begin{remark}
  The constructors of types \texttt{Rel} and \texttt{Fun} are suffixed by an underscore, in order to reserve the names \texttt{a}, \texttt{f}, \texttt{h}, \texttt{R}, etc. to functions which build terms and formulas (please look at Sect~\ref{sec:fol-term-notations} and \ref{sec:fol-atomic-notations}).
\end{remark}

@@

\begin{remark}[Variables]
In O'Connor's formalization of first-order logic, the variables are \gallina terms of the form \texttt{var $L$ $i$}, where $L$ is
 a language and $i$ a natural number. 
Although other choices may be considered : PHOAS, de Bruijn indices, etc,  we   respect this representation, in order not to break long proof scripts which use this representation (please look at \cite{OConnor05} for a related discussion).

@@

\subsubsection{Simplified notations for terms}
\label{sec:fol-term-notations}

 We can use \coq's \texttt{Notation} features to print and parse terms in a more readable form.

@@

\subsection{Notations for first-order formulas}

@@

\vspace{6pt}

\noindent From \href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}

\inputsnippets{fol/folScope}

\subsubsection{Simplified notations for atomic formulas}
\label{sec:fol-atomic-notations}

@@

\noindent From~\href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples}

\vspace{6pt}

@@

\begin{remark}[bound variables]

  In~\cite{Goedel}, there is no De Bruijn encoding of bound variables (see also~\cite{OConnor05}). The following example shows two formulas which share the same structure, are logically equivalent, but are not Leibniz equal.

\vspace{4pt}

\noindent From~\href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples}

\inputsnippets{FolExamples/boundVars}  
\end{remark}
